%! Authors = Eduardo Serna & Leo Diago-Cisneros

% Preamble
\documentclass{../assets/templates/iopjournal}
%\documentclass[twocolumn]{revtex4-2}

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amsmath,amssymb,graphicx,hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amssymb}
\usepackage{orcidlink}

\newcommand{\bn}[1]{\mbox{\boldmath $#1$}}
\newcommand{\mb}{\mbox}
\newcommand{\angstrom}{\textup{\AA}}

% Document
\begin{document}
%\articletype{Paper}

    \title{Channel-Interference and Spin-Orbit effects on Quantum Tunneling in Mono-layer Graphene}
    
    \author{Eduardo Serna$^1$\orcidlink{0000-0003-2090-7067}, L. Diago-Cisneros$^2$\orcidlink{0000-0001-9409-1545} and I. Rodr\'iguez-Vargas$^3$.}
    
    \affil{$^1$Centro de Investigación en Ciencias, Universidad Autónoma del Estado de Morelos, Av. Universidad 1001 Col. Chamilpa, 62209, Cuernavaca, Morelos, México; sernaed95@gmail.com}
       
    \affil{$^2$Facultad de Física, Universidad de La Habana, La Habana, 10400, Cuba}
    
    \affil{$^3$Unidad Académica de Ciencia y Tecnología de la Luz y la Materia, Universidad Autónoma de Zacatecas, Circuito Marie Curie S/N, Parque de Ciencia y Tecnología QUANTUM Ciudad del Conocimiento, 98160 Zacatecas, Zacatecas, México}
        
    \affil{$^*$L. Diago-Cisneros.Author to whom any correspondence should be addressed}
    \email{ldiago@fisica.uh.cu}
    
    \keywords{graphene, Rashba spin--orbit interaction, wave packets, electron transmission, spintronics}

% Abstract
    \begin{abstract}
        This theoretical study addresses the impact of channel interference (CI) and the Rashba spin-orbit interaction (SOIR) effects, on the transmission of Dirac-fermions (fD) throughout a potential barrier in monolayer graphene (MLG). Our findings reveal that the presence of SOIR significantly modifies fD transmission coefficients compared with those under pristine graphene conditions. Indeed, while quantum scattering in pristine graphene remains near unity, the introduction of SOIR leads to an intricate transmission patterns that depend mainly on the barrier parameters. The quantum transport phenomena are further complicated by channel interference between pseudospinor components, which manifest themselves as cross-coupling terms in the probability current density and significantly influence the scattering behavior of the MLG. These effects arise from the spin degeneracy lifting and spin-dependent scattering mechanisms. We hope that our outcomes supported by the suggested layered device with a gate-voltage embedded MLG, will emphasize enough the critical role of both the SOIR and the CI in forthcoming engineering of potential Spintronics as well as Quantum Computing devices.
    \end{abstract}


% Table of Contents (optional)
%    \tableofcontents
%    \newpage

% Introduction
    \section{Introductory Overview}\label{sec:introduction}
    \input{introduction02}

% Development
    \section{Theoretical Development}\label{sec:development}
    \input{development02}

% Discussion
    \section{Discussion of Results}\label{sec:discussion-of-results}
    \input{discussion02}

% Conclusion
    \section{Concluding Remarks}\label{sec:conclusions}

    In this work, we explored the effect of Rashba spin-orbit interaction (SOIR) on electronic transmission through a potential barrier in monolayer graphene using numerical simulations based on Gaussian wave packets and finite difference methods (FDM). The results revealed how the presence of the Rashba term introduces substantial and complex modifications to the transmission coefficients compared to the simple behavior observed in pristine graphene.
    These variations originate from spin-dependent scattering mechanisms, such as spin degeneracy lifting and quantum interferences derived from the multiple components of the wave packets used in our simulations.
    A key finding is the identification of channel interference effects between the pseudospinor components $\Psi_A$ and $\Psi_B$, which manifest as cross-coupling terms in the probability current density and fundamentally alter the transmission characteristics.

    Regarding the questions initially posed in this study, we successfully demonstrated that SOIR interactions do significantly modify transmission characteristics, thus affirmatively answering our initial inquiries.
    Additionally, we clarified that small deviations observed in pristine graphene from the theoretical unitary transmission are a direct consequence of the nature of the Gaussian packets employed, emphasizing the importance of considering these effects in simulations and practical applications.

    Collectively, our findings clearly highlight that a detailed understanding of SOIR provides predictive capability and essential tools for the engineering of spintronic devices and platforms applicable to quantum computing.
    Therefore, this study firmly reaffirms the relevance of these fundamental quantum phenomena in current and future technological scenarios. 
    
    Finally, we emphasize a key modeling choice: we neglect the canonical Dirac–Rashba term in pristine graphene because its magnitude is typically very small at the scales considered.
    Nevertheless, giant Rashba couplings have been reported in proximity-engineered systems (\textit{e.g.}, graphene on TMDs or with Au), for which the canonical term should be included explicitly and its impact on wave-packet propagation assessed.
    Extending our framework to that regime is straightforward (upgrade to a four-component spinor and add the Dirac–Rashba operator), and will be the subject of future work, where we will quantify the consequent spin splitting, spin precession, and possible Klein-to–anti-Klein transitions \cite{AvsarNatCommun2014, WangPhysRevX2016, DellAnnaJPhysCondMatt2018}.

% Acknowledgments
%\section*{Acknowledgments}
\ack{One of the authors (L.D-C) thanks for the support of DINVP and the hospitality of Departamento de Física y Matemáticas, Universidad Iberoamericana, Mexico City.}

\section*{Declaration on Generative AI}
\label{sec:genai}

This paper has been prepared with the assistance of several generative AI, for the sake of the grammar and clarity text improvements. Following the use of this tools, the authors thoroughly reviewed and edited the content as needed, and take full responsibility for the final version of the publication.

\bibliographystyle{unsrt}
\bibliography{bib/main}

\end{document}
